Model validation plots

### 2021-08-11 doc/validate_models.Rmd
switch to binned residuals plot using arm package

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## target knits Rmds in their own session, so load libraries here.
library(targets)
library(statmod)
library(tidyverse)
library(gratia)
library(mgcv)
library(dlnm)
```

@@

```{r echo=TRUE}
s_1ha_res <- qresid(s_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(s_1ha_res))
#QQ plot
qqnorm(s_1ha_res); qqline(s_1ha_res)
#Fitted vs. residuals
scatter.smooth(predict(s_1ha, type = "response"), s_1ha_res, col = "grey")
```
```{r}
# gam.check(s_1ha)
```

@@

```{r echo=TRUE}
s_cf_res <- qresid(s_cf)
par(mfrow = c(2,2))
#histogram
plot(density(s_cf_res))
#QQ plot
qqnorm(s_cf_res); qqline(s_cf_res)
#Fitted vs. residuals
scatter.smooth(predict(s_cf, type = "response"), s_cf_res, col = "grey")
```

@@

```{r}
f_1ha_res <- qresid(f_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(f_1ha_res))
#QQ plot
qqnorm(f_1ha_res); qqline(f_1ha_res)
#Fitted vs. residuals
scatter.smooth(predict(f_1ha, type = "response"), f_1ha_res, col = "grey")
```

@@

```{r}
f_cf_res <- qresid(f_cf)
par(mfrow = c(2,2))
#histogram
plot(density(f_cf_res))
#QQ plot
qqnorm(f_cf_res); qqline(f_cf_res)
#Fitted vs. residuals
scatter.smooth(predict(f_cf, type = "response"), f_cf_res, col = "grey")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## target knits Rmds in their own session, so load libraries here.
library(targets)
library(statmod)
library(tidyverse)
library(gratia)
library(mgcv)
library(dlnm)
library(arm)
```

@@

```{r echo=TRUE}
s_1ha_res <- qresid(s_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(s_1ha_res))
#QQ plot
qqnorm(s_1ha_res); qqline(s_1ha_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(s_1ha), residuals(s_1ha, type = "response"))
```
```{r}
# gam.check(s_1ha)
```

@@

```{r echo=TRUE}
s_cf_res <- qresid(s_cf)
par(mfrow = c(2,2))
#histogram
plot(density(s_cf_res))
#QQ plot
qqnorm(s_cf_res); qqline(s_cf_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(s_cf), residuals(s_cf, type = "response"))
```

@@

```{r}
f_1ha_res <- qresid(f_1ha)
par(mfrow = c(2,2))
#histogram
plot(density(f_1ha_res))
#QQ plot
qqnorm(f_1ha_res); qqline(f_1ha_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(f_1ha), residuals(f_1ha, type = "response"))
```

@@

```{r}
f_cf_res <- qresid(f_cf)
par(mfrow = c(2,2))
#histogram
plot(density(f_cf_res))
#QQ plot
qqnorm(f_cf_res); qqline(f_cf_res)
#Fitted vs. residuals--binned residuals plot
binnedplot(fitted(f_cf), residuals(f_cf, type = "response"))
```
